Panel Seminars

### 2022-07-08 index.Rmd
Updated intro page

The MarineOmics working group is part of the [RCN for Evolution in Changing Seas](https://rcn-ecs.github.io/), and was formed to promote **reproducible** and **robust** genomic research in nonmodel species, but especially marine and aquatic studies. Methods in next generation sequencing and bioinformatics advance at a pace that quickly render any static set of best practices obsolete. MarineOmics aims to support robust genomic research in ecology and evolution by disseminating guidelines through this dynamic, open-sourced website addressing introductory and advanced topics of population- and functional genomics.

@@

On this website you will find a growing and evolving collection of guidelines, tutorials, recommended readings, and method evaluations for various 'omics analyses that are commonly used in studies of nonmodel systems (particularly marine species). Instead of providing rigid "best practices", we aim to encourage data exploration and rigorous quality control through "best principles", paying particular attention to topics for which open access guidelines are scarce. The guidelines are written by members of the MarineOmics working group or the community, then shared for peer review. Comments on current website content or suggestions for new content can be made through the [Discussion Forum](https://github.com/MarineOmics/marineomics.github.io/discussions).

@@

### The guidelines portion of the website is still under peer review and should be considered a "preprint". If you are interested in contributing to the peer review process, check out the [Discussion Forum](discussion.html). {.unlisted .unnumbered}

@@

# Reproducibility in Marine Genomics  
Marineomics is also interested in evaluating and improving reproducibility in studies that use genomics to study adaptation in marine systems. We are conducting a meta-analysis of reproducibility across genomic studies of environmental adaptation in marine populations with the aim of identifying obstacles and opportunities for reproducing and synthesizing population genomic research. In Spring 2021, three undergraduate research interns contributed to this literature survey, with funding from the [RCN-ECS](https://rcn-ecs.github.io/).

# Working Group Members

@@

# Contact 
For any and all inquiries about the MarineOmics Working Group, our website and its material, or other activities, please contact us at rcnecs.marineomics@gmail.com.

>>>>

@@

On this website you will find a growing and evolving collection of guidelines, tutorials, recommended readings, and method evaluations for various 'omics analyses that are commonly used in studies of nonmodel systems (particularly marine species). Instead of providing rigid "best practices", we aim to encourage data exploration and rigorous quality control through "best principles", paying particular attention to topics for which open access guidelines are scarce. The guidelines are written by members of the [MarineOmics working group](#marineomics) or the community, then shared for peer review. Comments on current website content or suggestions for new content can be made through the [Discussion Forum](https://github.com/MarineOmics/marineomics.github.io/discussions).

@@

### The guidelines portion of the website should be considered a "preprint". If you are interested in contributing to the peer review process, check out the [Discussion Forum](discussion.html). {.unlisted .unnumbered}

@@

# What is the MarineOmics working group? {#marineomics}

The original MarineOmics working group is part of the [RCN for Evolution in Changing Seas](https://rcn-ecs.github.io/), and was formed to promote **reproducible** and **robust** genomic research in nonmodel species, but especially marine and aquatic studies. Methods in next generation sequencing and bioinformatics advance at a pace that quickly render any static set of best practices obsolete. MarineOmics aims to support robust genomic research in ecology and evolution by disseminating guidelines through this dynamic, open-sourced website addressing introductory and advanced topics of population- and functional genomics. *We are always looking for folks to join and write content for the website, if interested please [contact us](#contact)!*

# Reproducibility in Marine Genomics  
MarineOmics is also interested in evaluating and improving reproducibility in studies that use genomics to study adaptation in marine systems. We are conducting a meta-analysis of reproducibility across genomic studies of environmental adaptation in marine populations with the aim of identifying obstacles and opportunities for reproducing and synthesizing population genomic research. In Spring 2021, three undergraduate research interns contributed to this literature survey, with funding from the [RCN-ECS](https://rcn-ecs.github.io/).

# Original Working Group Members

@@

# Contact {#contact}
For questions about the website and its materials, post to the [Discussion Forum](https://github.com/MarineOmics/marineomics.github.io/discussions)!
For inquiries about the MarineOmics Working Group activities, please contact us at rcnecs.marineomics@gmail.com.
